Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/methods.tex
formatting revisions
edits

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{build.PNG}
	\caption{(a) Single monomers are parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and place in a monoclinic unit cell}\label{fig:python}
\end{figure}

A typical simulation volume contains four pores in a monoclinic unit cell,
the smallest unit cell that maintains hexagonal symmetry when extended 
periodically. Each pore is made of twenty stacked monomer layers with
% describe unit cell in terms of alpha beta gamma angles?
% mention semi-isotropic pressure coupling here or later
periodic continuity in all directions, avoiding any edge effects and 
creating an infinite length pore ideal for studying transport. A small
number of layers is preferred in order to reduce computational cost and 
to allow us to look at longer timescales. Ultimately, we chose to build a system
with 20 monomer layers in each pore in order to give sufficient
resolution when simulating X-ray diffraction patterns.  % BJC: reword / mention xrd resolution - system size dependence in previous sentence

@@

Initial guesses for the remaining structural parameters were chosen
based on experimental data and treated as variables during model
development. The distance between pores was based on experimental SAXS
data for this system \cite{feng_thin_2016}. Initial configuration pore
spacing was chosen to be 10 \% larger than the experimental value to reduce
unintended repulsions resulting from a tightly packed initial configuration. 
The layer spacing was based on experimental 2D WAXS data which shows
reflections corresponding to features spaced 3.7 \angstrom apart. It has 
been hypothesized that the features are present due to pi-pi
interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
Our simulations tend to equilibrate to a wider interlayer spacing of $\approx$ 4.1 \angstrom,
which inspired separate systems starting with layer spacings greater than
 4 \angstrom. Initial pore radius estimates of 0.6 nm were based on past TEM 
images and size exclusion rejection data\cite{feng_scalable_2014,
feng_thin_2016,zhou_supported_2005}.
% There is plenty I can say about initial configuration. Starting layers
% too far apart, too close, tilted initial configurations etc.
The relative interlayer orientation was chosen based on clues from diffraction
data as well as the various known stacking modes of benzene and substituted 
benzene rings: sandwiched, parallel-displaced and T-shaped 
(\Cref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
configuration was ruled out based on the inconsistency of its $\approx$ 
5 \angstrom equilibrium stacking distance. The system's preference
towards the sandwiched vs. parallel displaced stacking modes was left
to be explored. Visualization of each configuration 
(\Cref{fig:sandwichedlayers,fig:offsetlayers}) suggests 
entropic differences based on the way the tails are able to pack. 
This difference may explain, in part, which stacking mode is more favorable.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{Sandwiched}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{Parallel-Displaced}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{T-shaped}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{Two monomer layers stacked in the sandwiched configuration}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{Two monomer layers stacked in the parallel-displaced configuration}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{}\label{fig:stacking}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG}
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
\end{figure}

A typical simulation volume contains four pores in a monoclinic unit cell,
the smallest unit cell that maintains hexagonal symmetry when extended 
periodically. Each pore is made of twenty stacked monomer layers with
% describe unit cell in terms of alpha beta gamma angles?
% mention semi-isotropic pressure coupling here or later
periodic continuity in all directions, avoiding any edge effects and 
creating an infinite length pore ideal for studying transport. A small
number of layers is preferred in order to reduce computational cost and 
to allow us to look at longer timescales. Ultimately, we chose to build a 
system with 20 monomer layers in each pore in order to   
obtain sufficient resolution when simulating X-ray diffraction patterns.
This point will be explained in more detail later. 
% BJC: reword / mention xrd resolution - system size dependence in previous sentence

@@

Initial guesses for the remaining structural parameters were chosen
based on experimental data and treated as variables during model
development. The distance between pores was based on experimental SAXS
data for this system \cite{feng_thin_2016}. Initial configuration pore
spacing was chosen to be 10 \% larger than the experimental value to reduce
unintended repulsions resulting from a tightly packed initial configuration. 
The layer spacing was based on experimental 2D WAXS data which shows
reflections corresponding to features spaced 3.7 \angstrom apart. It has 
been hypothesized that the features are present due to pi-pi
interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
Our simulations tend to equilibrate to a wider interlayer spacing of $\approx$ 4.1 \angstrom,
which inspired separate systems starting with layer spacings greater than
 4 \angstrom. We estimate the pore radius to be 0.6 nm based on past TEM 
images and size exclusion rejection data\cite{feng_scalable_2014,
feng_thin_2016,zhou_supported_2005}. Comparing a geometric
measurement of pore size taken from an atomistic model, to a less
precise, experimentally derived pore size estimate, will give ambiguous
results. When constructing pores, we chose the carboxylate carbon from
the monomer head group as a reference atom, and placed it a distance r from the
pore center, where r is the pore radius. We will not make direct comparisons
of pore radius between our model and experiment to avoid the ambiguity. 
% There is plenty I can say about initial configuration. Starting layers
% too far apart, too close, tilted initial configurations etc.
The relative interlayer orientation was chosen based on clues from diffraction
data as well as the various known stacking modes of benzene and substituted 
benzene rings: sandwiched, parallel-displaced and T-shaped ~\cite{sinnokrot_estimates_2002}
(\Cref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
configuration was ruled out based on the inconsistency of its $\approx$ 
5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}. The system's preference
towards the sandwiched vs. parallel displaced stacking modes was left
to be explored. Visualization of each configuration 
(\Cref{fig:sandwichedlayers,fig:offsetlayers}) suggests 
entropic differences based on the way the tails are able to pack.
In the sandwiched configuration, all tails start out directly on top 
of each other which may prevent closely stacked benzene rings. In the offset
configuration, the tails in between each other which may allow layers
to come together in a compact way. This difference may explain, in part,
which stacking mode is more favorable.

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{Sandwiched benzene dimers stack 3.8 \anstrom apart}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{Parallel-Displaced benzene dimers stack 3.4 \angstrom vertically and 1.6 \angstrom horizontally apart}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{T-shaped benzene dimers stack 5.0 \angstrom apart}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{Two monomer layers stacked in the sandwiched configuration}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{Two monomer layers stacked in the parallel-displaced configuration}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{}\label{fig:stacking}
\end{figure}
